Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2023-01-11 index.Rmd
Update index
new version figure 3, new figures in supplement

[The repository on github.](https://github.com/UZH-PEG/diversity_envresp1)

[The respository on Zenodo with DOI 10.5281/zenodo.6334544.](https://doi.org/10.5281/zenodo.6334544)

>>>>

[The repository on github, current version 0.9.1.](https://github.com/UZH-PEG/diversity_envresp1/releases/tag/0.9.1)

[The respository on Zenodo with DOI 10.5281/zenodo.7360272
](https://zenodo.org/record/7360272#.Y4CXmOzMJqs)

### 2023-01-11 reports/supplement/supplement_0.9.1.Rmd
new version figure 3, new figures in supplement

(ref:div-repl-meth1) **Replication method results.** **Left column of panels**: the effect of trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient. The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only. The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations. Data is missing in panels e, and i, when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g. when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities). **Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience.

@@

sim_length <- 1e6 ## currently a problem in how sim length is parsed by the data processing step
num_strains <- 9
plot_here <- all_stab %>%
  filter(simlength == sim_length) %>%
  ## remove data where there are non-standard stable states
## this subset is identified by inspection of stable state figures
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.70),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))

p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

(ref:div-temp-eventdef1) **Results with an abundance floor.** **Left column of panels**: the effect of trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient. The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only. The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations. **Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e. delayed the shift to the other state.

@@

wait_time <- 1e6
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))

p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

wait_time <- 1e6
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

wait_time <- 1e5
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2
```

@@

wait_time <- 1e4
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2
```

@@

```{r div-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth4)', fig.height=7, fig.width=6, fig.align="center"}
wait_time <- 1e3
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2
```

@@

wait_time <- 1e2
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00))
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(wait_time,
                                                           " wait time,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2
```

@@

(ref:div-stab-multstrain1)  Effects of number of strains and of diversity among strains.

@@

plot_here111 <- all_stab %>%
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00),

         !(num_strains == 6 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 6 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 6 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 6 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 6 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 6 & var_treat == "SB-PB" & stand_var > 1.00),
         !(num_strains == 6 & var_treat == "CB-SB-PB" & stand_var > 1.00),

         !(num_strains == 3 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 3 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 3 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 3 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 3 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 3 & var_treat == "SB-PB" & stand_var > 1.0),
         !(num_strains == 3 & var_treat == "CB-SB-PB" & stand_var > 1.00),

         !(num_strains == 2 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 2 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 2 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 2 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 2 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 2 & var_treat == "SB-PB" & stand_var > 1.00),
         !(num_strains == 2 & var_treat == "CB-SB-PB" & stand_var > 1.00))

fig_div_vs_o2diff_multistrain(plot_here111, which_strains,
                              which_wait_time, figure_title)
```

@@

(ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present.

@@

## remove data where there are non-standard stable states
## this subset is identified by inspection of stable state figures
plot_here11 <- all_stab %>%
  filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
         !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
         !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
         !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00),
         !(num_strains == -1 & var_treat == "CB" & stand_var > 1.00),
         !(num_strains == -1 & var_treat == "SB" & stand_var > 0.60),
         !(num_strains == -1 & var_treat == "PB" & stand_var > 1.00),
         !(num_strains == -1 & var_treat == "CB-SB" & stand_var > 0.60),
         !(num_strains == -1 & var_treat == "CB-PB" & stand_var > 1.00),
         !(num_strains == -1 & var_treat == "SB-PB" & stand_var > 1.00),
         !(num_strains == -1 & var_treat == "CB-SB-PB" & stand_var > 1.00))

plot_1 <- fig_div_vs_o2diff_maxtolcomp(plot_here11, which_strains,
                              which_wait_time, figure_title)
plot_1 +
  xlab("Standardised amount of trait variation used to create nine strains\nof which either all nine are retained, or only the most tolerant is retained.") +
  guides(col=guide_legend(title="Which strains are retained", title.position = "top"))
```

>>>>

(ref:div-repl-meth1) **Replication method results.** **Left column of panels**: the effect of trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient. The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only. The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations. In panels e, and i, the orange region shows when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g. when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities). **Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience.

@@

sim_length <- 1e6 ## currently a problem in how sim length is parsed by the data processing step
num_strains <- 9

plot_here <- all_stab %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "PB" & stand_var > 0.69) ~ "non-standard",
          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

(ref:div-temp-eventdef1) **Results with an abundance floor.** **Left column of panels**: the effect of trait diversity (y-axis) on the positions of the tipping points (anoxic to oxic in blue, oxic to anoxic in red), which determine the extent of the region of bistability (green shaded region) in the oxygen diffusivity gradient. The left-most region is anoxic only, the middle is oxic or anoxic depending on historical conditions, and the right-most is oxic only. The thick grey vertical lines at -8 and 0 on the x-axis show the extent of the oxygen diffusivity gradient investigated in the simulations. In panels e, and i, the orange region shows when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g. when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities). **Right column of panels**: The effect size of trait variation on resilience, with positive values on the y-axis indicating that diversity has increased resilience, i.e. delayed the shift to the other state.

@@

wait_time <- 1e6
num_strains <- 9

plot_here <- all_stab %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

wait_time <- 1e6
num_strains <- 9

plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

wait_time <- 1e5
num_strains <- 9

plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

wait_time <- 1e4
num_strains <- 9

plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

```{r div-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth4)', fig.height=7, fig.width=6, fig.align="center"}
wait_time <- 1e3
num_strains <- 9

plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

wait_time <- 1e2
num_strains <- 9

plot_here <- all_stab %>%
  filter(waittime == wait_time) %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

p1 <- fig_div_vs_o2diff_1strain_7row_stable_state_type(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

(ref:div-stab-multstrain1)  Effects of number of strains and of diversity among strains. In panels PB and CB-PB the region with dashed lines shows when patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g. when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).

@@

plot_here111 <- all_stab %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

# plot_here111 <- all_stab %>%
#   filter(!(num_strains == 9 & var_treat == "CB" & stand_var > 1.00),
#          !(num_strains == 9 & var_treat == "SB" & stand_var > 1.00),
#          !(num_strains == 9 & var_treat == "PB" & stand_var > 0.65),
#          !(num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00),
#          !(num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65),
#          !(num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.0),
#          !(num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00),
#          
#          !(num_strains == 6 & var_treat == "CB" & stand_var > 1.00),
#          !(num_strains == 6 & var_treat == "SB" & stand_var > 1.00),
#          !(num_strains == 6 & var_treat == "PB" & stand_var > 0.65),
#          !(num_strains == 6 & var_treat == "CB-SB" & stand_var > 1.00),
#          !(num_strains == 6 & var_treat == "CB-PB" & stand_var > 0.65),
#          !(num_strains == 6 & var_treat == "SB-PB" & stand_var > 1.00),
#          !(num_strains == 6 & var_treat == "CB-SB-PB" & stand_var > 1.00),
#          
#          !(num_strains == 3 & var_treat == "CB" & stand_var > 1.00),
#          !(num_strains == 3 & var_treat == "SB" & stand_var > 1.00),
#          !(num_strains == 3 & var_treat == "PB" & stand_var > 0.65),
#          !(num_strains == 3 & var_treat == "CB-SB" & stand_var > 1.00),
#          !(num_strains == 3 & var_treat == "CB-PB" & stand_var > 0.65),
#          !(num_strains == 3 & var_treat == "SB-PB" & stand_var > 1.0),
#          !(num_strains == 3 & var_treat == "CB-SB-PB" & stand_var > 1.00),
#          
#          !(num_strains == 2 & var_treat == "CB" & stand_var > 1.00),
#          !(num_strains == 2 & var_treat == "SB" & stand_var > 1.00),
#          !(num_strains == 2 & var_treat == "PB" & stand_var > 0.65),
#          !(num_strains == 2 & var_treat == "CB-SB" & stand_var > 1.00),
#          !(num_strains == 2 & var_treat == "CB-PB" & stand_var > 0.65),
#          !(num_strains == 2 & var_treat == "SB-PB" & stand_var > 1.00),
#          !(num_strains == 2 & var_treat == "CB-SB-PB" & stand_var > 1.00))

fig_div_vs_o2diff_multistrain_stable_state_type(plot_here111, which_strains,
                              which_wait_time, figure_title)
```

@@

(ref:max-tol1) Effects of strain variation on position of tipping points compared between simulations with all (nine) strains present and simulations where only the most tolerant strain is present. When tipping points are shown with dashed lines then patterns of coexistence were atypical of the classical pattern shown in Figure 1a of the main text (e.g. when cyanobacteria coexisted with sulfur bacteria at low oxygen diffusivities).

@@

plot_here11 <- all_stab %>%
  mutate(stab_states_type = "standard",
         stab_states_type = case_when(
          (num_strains == 9 & var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == 9 & var_treat == "SB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == 9 & var_treat == "PB" & stand_var > 0.65) ~ "non-standard",
          (num_strains == 9 & var_treat == "CB-SB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == 9 & var_treat == "CB-PB" & stand_var > 0.65) ~ "non-standard",
          (num_strains == 9 & var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == 9 & var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard",

          (num_strains == -1 & var_treat == "CB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "SB" & stand_var > 0.60) ~ "non-standard",
          (num_strains == -1 & var_treat == "PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-SB" & stand_var > 0.60) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "SB-PB" & stand_var > 1.00) ~ "non-standard",
          (num_strains == -1 & var_treat == "CB-SB-PB" & stand_var > 1.00) ~ "non-standard"
         ),
         stab_states_type = ifelse(is.na(stab_states_type), "standard", "non-standard")
  )

plot_1 <- fig_div_vs_o2diff_maxtolcomp_stable_state_type(plot_here11, which_strains,
                              which_wait_time, figure_title)
plot_1 +
  xlab("Standardised amount of trait variation used to create nine strains\nof which either all nine are retained, or only the most tolerant is retained.") +
  guides(col=guide_legend(title="Which strains are retained", title.position = "top"))
